---
title: "Conventional Possibility"
author: "Jonathan Phillips & Maeen Arslan"
date: "November 2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
csl: apa.csl
word_document: default
---
  
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,dpi=300,fig.width=7)

#rm(list=ls())

blackGreyPalette <- c("#2C3539", "#999999") 
library(tidyverse)
library(lme4)
library(knitr)
library(grid)

```

## Study 1 "Possibility Study"
```{r data study 1, echo=FALSE}
d<- read.csv("data/study1_possibility.csv", stringsAsFactors = F)
```

We collected a sample of `r length(unique(d$id))` participants ($M_{age}$ = `r round(mean(d$age,na.rm=T),digits=2)`; $SD_{age}$ = `r round(sd(d$age,na.rm=T),digits=2)`; `r table(d$sex)[[1]]` females) from Amazon Mechanical Turk ([www.mturk.com]( www.mturk.com)).




```{r norming cleaning, echo=FALSE, message=FALSE}
#Cleaning the dataframe
# Selecting relevant variables
d <- d[d$condition1 != "na",]
d <- d[d$response != "timeout",]
d$condition1[d$condition1 == "flouting"] <- "abnormal"

d$response <- factor(d$response, levels = c("f", "j"))
d$response <- as.numeric(d$response) - 1

## Cutting out respondents who were too fast

d.exclude <- d %>% filter(RT < 6000) %>%
  group_by(condition3,id) %>%
  summarise(meanRT = mean(RT, na.rm = T),
            sdRT = sd(RT, na.rm = T))

fast.excluded <- d.exclude$id[d.exclude$condition3=="fast" & d.exclude$meanRT<800]
slow.excluded <- d.exclude$id[d.exclude$condition3=="slow" & d.exclude$meanRT<1000]

d <- d %>% filter( !(id %in% fast.excluded | id %in% slow.excluded)) %>%
  filter( !(condition3=="slow" & RT < 1500)) %>%
  filter( !(RT < 500))

## Correcting trial number

just_group1.0 <- d[d$subjectGroup == "1",]
just_group1 <- just_group1.0 %>% group_by(target,trialNo) %>% summarize(n = length(trialNo))

# If X and subject group 1 have the same target, they should also have the same trial number

i = 1
j = 1

while (i <= length(d$trialNo)){
  if (d$subjectGroup[i] != "1"){
    while (j <= length(just_group1$target)){
      if (d$target[i] == just_group1$target[j]){
        d$trialNo[i] <- just_group1$trialNo[j]
      }
      j <- j + 1
    }
  }
  i <- i + 1
  j = 1
}

```



### Procedure

Subjects made judgements about the same 128 actions, labeling them either possible or
impossible by pressing the corresponding key on their keyboard. Each subject judged four
scenarios and their corresponding actions under time pressure (1.5 seconds) and judged the
remaining four scenarios and their corresponding actions with no time pressure. In the slow
trials, subjects were encouraged to reflect on their answers. The combination of scenarios
represented in each fast and slow group were randomized using a Latin-square design. Subjects
were randomly assigned to one of the eight conditions created by this randomization scheme.

Trials for which the response time was too fast, trials that timed out, and trials with not
applicable responses were excluded. The final dataset consisted of 15,991 trials. There were
4157 abnormal trails, 4110 immoral trials, 3902 impossible trials, and 3822 ordinary trials,
divided across 10,268 fast trials and 5723 slow trials.

```{r analysis, echo=FALSE, message=FALSE}
#Analyzing Data
## Summarized dataframe
d.sum <- d %>% group_by(condition1,condition3,trialNo) %>% summarize(
  N = length(response),
  mean = mean(response, na.rm=TRUE),
  sd = sd(response, na.rm=TRUE),
  se = sd / sqrt(N))

d.slow <- d %>% filter(condition3 == "slow") %>%
  group_by(condition1) %>%
  summarize(
    mean = mean(response, na.rm = TRUE),
    sd = sd(response, na.rm = TRUE)
  )
## Joint norming + possibility dataframe - wide

d.sum2 <- d %>% group_by(trialNo, target, condition1, condition3) %>% 
  summarise(
    mean = mean(response, na.rm=TRUE),
    sd = sd(response, na.rm=TRUE),
    N = length(response),
    se = sd / sqrt(N)
  ) %>%
  pivot_wider(names_from= condition3, values_from= c(mean,sd,N,se)) 

norms <- read.csv("data/normingmeans3.csv", stringsAsFactors = F)
d.norms <- full_join(d.sum2,norms,by="trialNo") # all event types

d.norms <- mutate(d.norms, FminusS = mean_fast - mean_slow)
#write.csv(d.norms,file="possibilityAnalysis.csv")
## Joint norming + possibility dataframe - long

d.sum3 <- d %>% group_by(trialNo, target, condition1, condition3) %>% 
  summarise(
    mean = mean(response, na.rm=TRUE),
    sd = sd(response, na.rm=TRUE),
    N = length(response),
    se = sd / sqrt(N)
  )

d.norms3 <- full_join(d.sum3,norms,by=c("trialNo")) # all types
write.csv(d.norms3, file="study1and2.csv")
d1 <- read.csv("Convention Data Files/Pilot_results4.csv",stringsAsFactors = F) #needed for end variable of d.norms4
d1p <-d1[!duplicated(d1$id),]
d.means4 <- d1 %>% filter(response!=6) %>% 
  group_by(condition1,subjectGroup, trialNo) %>%
  summarize(N = length(response),
            mean = mean(response, na.rm = T),
            sd = sd(response, na.rm =T),
            se = sd / sqrt(N)
  ) 


d.norms4 <- full_join(d.sum3,d.means4,by="trialNo") # extra long
## Modeling

# Overall effect
lm1.0 <- glmer(response ~ condition1 * condition3 + (1|id) + (1|condition2), data=d, family = "binomial", control = glmerControl(optimizer = c("optimx"), optCtrl = list(method = "nlminb")))
summary(lm1.0)

# Interaction: Significant interaction effect (chisq=204.58, df=3, p<2.2e-16)
lm1.1 <- glmer(response ~ condition1 + condition3 + (1|id) + (1|condition2), data=d, family = "binomial",  control = glmerControl(optimizer = c("optimx"), optCtrl = list(method = "nlminb")))
anova(lm1.0,lm1.1)

# Main effect of deliberation: None (chisq=.024, df=1, p=.876)
lm1.2 <- glmer(response ~ condition1 + (1|id) + (1|condition2), data=d, family = "binomial",  control = glmerControl(optimizer = c("optimx"), optCtrl = list(method = "nlminb")))
anova(lm1.1,lm1.2)

# Main effect of event-type: Yes (chisq==6225.7, df=3, p<2.2e-16)
lm1.3 <- glmer(response ~ condition3 + (1|id) + (1|condition2), data=d, family = "binomial", control = glmerControl(optimizer = c("optimx"), optCtrl = list(method = "nlminb")))
anova(lm1.1,lm1.3)

# Effect of deliberation for each event type (also evident in fig2a)
#       Ordinary: Main effect (z=-6.591, p<2e-16)
summary(glmer(response ~ condition3 + (1|id) + (1|condition2), data=d[d$condition1=="ordinary",], family = "binomial"))
#       Abnormal: No main effect (z=0.495, p<0.621)
summary(glmer(response ~ condition3 + (1|id) + (1|condition2), data=d[d$condition1=="abnormal",], family = "binomial"))
#       Impossible: Main effect (z=10.82, p<2e-16)
summary(glmer(response ~ condition3 + (1|id) + (1|condition2), data=d[d$condition1=="impossible",], family = "binomial"))
#       Immoral: Main effect (z=-5.621, p=1.9e-08)
summary(glmer(response ~ condition3 + (1|id) + (1|condition2), data=d[d$condition1=="immoral",], family = "binomial"))

d.1.3 <- d %>% group_by(condition1,condition3) %>%
  summarize(
    possibility = mean(response)
  )
```
### Results
